Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-26 paper/galsize_paper.tex
Minor edits to 4.4

We now examine how galaxy clustering depends on size when we control both for stellar mass and color dependence of galaxy clustering. Using the $\mstar>10^{10.25}\msun$ sample used above, we first divide the sample into ``red" and ``blue" subsamples using $g-r=0.65$ as a boundary, which approximately corresponds to the trough of the green valley for this stellar mass. For each color-selected subsample, we separately measure $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}},$ and use these median size values to split each subsample into two.

>>>>

We now examine how galaxy clustering depends on size when we control both for stellar mass and color dependence of galaxy clustering. Using a volume-limited galaxy sample with $10^{9.75}\msun < \mstar< 10^{10.25}\msun,$ we first divide the sample into ``red" and ``blue" subsamples using $g-r=0.65$ as a boundary, which approximately corresponds to the trough of the green valley for this stellar mass. For each color-selected subsample, we separately measure $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}},$ and use these median size relations to split each subsample into two.
